Double Trouble: Understanding Sex Differences in Synthetic Lethal interactions in Human Cancers \\~\\ Summer Wrap Up

### 2023-08-07 aug08meeting_pres4/may30ccgmeeting.tex
updates

		  		\begin{block}{} Overall Objective and Approach \end{block}
		  		\begin{block}{} Synthetic Lethality Analysis Update \end{block}
		  		\begin{block}{} Limitations of the Study \end{block}
		  		\begin{block}{} Next Steps/Future Work \end{block}
		  		\begin{block}{} Takeaways \& Tips for Future Undergrads \end{block}

@@

	\begin{frame}{Overall Objective}
		\begin{itemize}
			%\includegraphics[width=11cm, height=6cm]{types_of_courses_taken.jpg}
			\item Can we build sex-specific synthetic lethality networks for various cancer types? \newline

@@

	\section{Approach}
	\begin{frame}{Overall Project Workflow}
		\includegraphics[width=12cm, height=8cm]{project_workflow_slpmcrc_2.png}
	\end{frame}

	\section{Synthetic Lethality}
	\begin{frame}{Using DE Genes to Find Sex-Specific Synthetic Lethal Pairs}
		\begin{center}
			\includegraphics[width=7cm, height=4cm]{all_cancersvenndiagram_malede_vs_femalede_0.9.png}
		\end{center}
		\begin{enumerate}
			\item Find all potential gene pair combinations using differentially expressed genes \newline	
			\textcolor{blue}{${1289 \choose 2 } = 830,116$ Downregulated Male Pairs \newline}
			\textcolor{yellow}{${892 \choose 2 } = 397,386$ Downregulated Female Pairs}

@@

	\begin{frame}{Fishers Exact Test}

>>>>

		  		\begin{block}{} Overall Objective and Approach \end{block}
		  		\begin{block}{} Synthetic Lethality Analysis Update \end{block}
		  		\begin{block}{} Next Steps/Future Work \end{block}
		  		\begin{block}{} Limitations of the study \end{block}
		  		\begin{block}{} Takeaways \& Tips for Future Undergrads \end{block}

@@

	\section{Overall Objective and Approach}
	\begin{frame}{Overall Objective}
		\begin{itemize}
			%\includegraphics[width=11cm, height=6cm]{types_of_courses_taken.jpg}
			\item Can we build sex-specific synthetic lethality networks for various cancer types? \newline

@@

	\begin{frame}{Overall Project Workflow}
		\includegraphics[width=12cm, height=8cm]{project_workflow_slpmcrc_2.png}
	\end{frame}

	\section{Synthetic Lethality Analysis Update}
	\begin{frame}{Using DE Genes to Find Sex-Specific Synthetic Lethal Pairs}
		\begin{center}
			\includegraphics[width=7cm, height=4cm]{all_cancersvenndiagram_malede_vs_femalede_0.9.png}
		\end{center}
		\begin{enumerate}
			\item Find all potential gene pair combinations using differentially expressed genes \newline	
			\textcolor{blue}{${1289 \choose 2 } = 830,116$ Potential Male Pairs \newline}
			\textcolor{yellow}{${892 \choose 2 } = 397,386$ Potential Female Pairs}

@@

	\begin{frame}{Fishers Exact Test}
		Used to determine association between two categorical variables (overexpression and underexpression) when dealing with small sample sizes
		\begin{center}
		\includegraphics[width=10cm, height=7cm]{Contingency.png}
		\end{center}
	\end{frame}

	\begin{frame}{Ranking Genes by Number of Interactions}
		\includegraphics[width=12cm, height=5cm]{interactions.png}

		\begin{itemize}
		\item ISLE Method SL list Matches: Males = 14 pairs, Females = 11 pairs
		\item Experimentally Validated SL list Matches: Males = 21 pairs, Females = 2 pairs
		\end{itemize}
	\end{frame}

	\section{Next Steps/Future Work}
	\begin{frame}{Next Steps for Synthetic Lethality Analysis}
		\begin{enumerate}
			\item Refine the current list of synthetic lethal pairs by performing survival analysis to identify SL pairs that contribute to improved patient survival.
			\item Build male and female synthetic lethal interaction networks
		\end{enumerate}
	\end{frame}

	\begin{frame}{}
		content...
	\end{frame}
